% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{amsart}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{realboxes}
\usepackage{titlesec}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
%\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Samuel L. Green}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
%\def\footerlink{http://sa.muel.green}
\def\footerlink{}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = blue,
  pdfauthor = {\name},
  pdfkeywords = {economics, statistics, mathematics},
  pdftitle = {\name: Resume},
  pdfsubject = {Resume},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=0.75in,
  bottom=0.4in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
%\usepackage{sectsty}
%\sectionfont{\rmfamily\mdseries\Large}
%\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

% Reduce space before sections and subsections
\titlespacing*{\section}{0pt}{0.7\baselineskip}{0.5\baselineskip}
\titlespacing*{\subsection}{0pt}{0.5\baselineskip}{0\baselineskip}

\begin{document}

% Place name at left
%{\huge \name}

% Alternatively, print name centered and bold:
\centerline{\huge \bf \name}

\vspace{0.1in}

\Centerline{
\begin{minipage}{0.45\linewidth}
\begin{flushright}
  1192 Park Avenue, Apt. 11B \\
  New York, NY \\
  10128 \\
\end{flushright}
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Phone: & (646) 457-2340 \\
    Email: & \href{mailto:s@muel.green}{s@muel.green} \\
    Homepage: & \href{http:/sa.muel.green/}{http://sa.muel.green/} \\
  \end{tabular}
\end{minipage}}

% % 
% % Education
% %
\section*{Education}

\subsection*{Harvard University} 
\begin{itemize}
\item Class of 2017. A.B. \textit{summa cum laude} in Computer Science, minor in Government.
\item Phi Beta Kappa, John Harvard Scholar (2014, 2016), Detur Book Prize (2014).  GPA 3.946. 
\end{itemize}

\subsection*{HBX, Harvard Business School}
\begin{itemize}
\item{Summer 2015. Credential of Readiness (CORe): coursework in accounting, business economics, and statistics. High honors.}
\end{itemize}

\subsection*{Phillips Academy, Andover}
\begin{itemize}
  \item Class of 2013. Cum Laude Society, Van Duzer prize for high scholarship, prizes in physics, history, Latin, biology, and math.  
\end{itemize}

\section*{Work Experience}

\subsection*{Bridgewater Associates, L.P. Investment Associate. (September 2017 -) }
\begin{itemize}
\item Beginning September 2017.
\end{itemize}

\subsection*{Harvard University. Head Teaching Fellow, Computer Science 51. (Fall 2015 - Spring 2017)}
\begin{itemize}
\item
Selected and led the 28-member teaching staff for the second introductory CS course, serving 400 students. Oversaw
development of problem sets, policies, and course infrastructure, including design and build of a software
system for on-campus attendance collection. Executed in Fall 2015 a re-design of the course,
including hiring, training, and managing staff to meet demands of a ''flipped classroom.''
\end{itemize}

\subsection*{BlackRock, Inc. Intern, Fixed Income Quantitative Portfolio Strategies. (Summer 2016)} 
\begin{itemize}
\item Conducted foreign exchange statistical arbitrage investment research in Julia using new quantitative investment research platform. 
Developed software for the platform as needed. 
\end{itemize}

\subsection*{BlackRock, Inc. Intern, Financial Modeling Group. (Summer 2015)}
\begin{itemize}
\item Designed and implemented a high-throughput server with multi-level caching architecture for security-level
and factor-level cumulative performance and attribution data. Placed second in intern class hack-a-thon,
building a UI tracking tool with one-line html integration with BlackRock web applications
\end{itemize}

\subsection*{The Phillipian. Editor in Chief. (2012)}
\begin{itemize}
\item Oversaw editorial processes and content creation, including staff editorials, for the independent 
weekly student newspaper of Phillips Academy, Andover. Managed business,
logistical, and technology operations, including a staff of more than 60 students. Turned operating loss
of \$6,000 into \$5,000+ profit on \$30,000+ annual revenue.
\end{itemize}


\section*{Technical Experience}
\subsection*{Computer Science Coursework}
\begin{itemize}
\item Abstraction and Design in Computation, Theory of Computation, Data Structures and Algorithms,
 Data Visualization, Network Analysis, Computation and Economics.
\end{itemize}
\subsection*{Statistics / Applied Math Coursework}
\begin{itemize}
\item Advanced Optimization, Data Science, Probability Theory, Inference, Time Series Analysis, Linear Modeling, Financial Statistics.  
\end{itemize}

\subsection*{Programming}
\begin{itemize} 
\item Data science and web development in Python, and experience in Julia, OCaml, Java, R, and C.
\end{itemize}

% Make lists without bullets and unindented
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{0em}
  }
}{
  \end{list}
}

\section*{Athletics \& Other}
\begin{itemize}
\item \textbf{The Oak Club}. President (2016), Treasurer (2015) of 65-student campus club.
\item \textbf{Harvard Varsity Crew} (Fall 2013 - Spring 2015). Varsity Four EARC Champion, Spring 2014.
\item \textbf{Spokes America} (Summer 2014). San Francisco to Washington D.C. cycling trip, teaching STEM.
\item \textbf{Shinnecock Hills Golf Club} (Summers 2009-2012). Caddie. 
\end{itemize}

\bigskip

% Footer
%\begin{center}
%  \begin{footnotesize}
%    Last updated: \today \\
%    \href{\footerlink}{\texttt{\footerlink}}
%  \end{footnotesize}
%\end{center}

\end{document}
